\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-09 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Changement .tex modèle

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs are strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings in two different ways.

First, we run a comparative statics analysis following a reduction in transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario, the reduction in total transport costs is solely attributable to the ad-valorem component (e.g., contrasting Table \ref{tab:calib_TC}, Column (3) to (1) for air transport, and Column (7) to (5) for maritime transport); in the second scenario, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. In this scenario, we contrast Table \ref{tab:calib_TC}, Column (4) to (2) (Air) and Column (8) to (6) (Vessel). Importantly, we run this comparative statics analysis \textit{ceteris paribus}, notably with the same value of the export fixed cost $f_x$ as in the initial equilibrium (see Table \ref{tab:calib_horsTC}.

@@

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (1)-(4)) and Vessel (Columns (5)-(8)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms. For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (1)-(2) for Air, (5)-(6) for Vessel), contrasting the case of only ad-valorem costs (Columns (1), (5)) and in presence of transport costs (Columns (2), (6)). In Columns (3)-(4) for Air and (7)-(8), we report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline  
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\ 
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline  
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

\subsubsection{Reducing international transport costs}

In this first exercise, we contrast the effects of a reduction of international transport costs depending on whether this occurs through a reduction in ad-valorem costs only, or a combined reduction in both the additive and the multiplicative components. In Table \ref{tab:resultats_modele}, this relies on the results reported in Column (A) versus (B) for Air, Column (E) versus (F) for Vessel.\medskip

Whatever the transport mode (and the associated magnitude of the transport costs decrease), welfare gains are higher when this reduction is partly achieved through a reduction of additive costs. The effect is substantial: The reduction of 3.4 percentage points of Air transport costs generates a welfare gain higher by 0.58 percentage point when such a reduction occurs through the additive component (accounting for almost 60\% of the total cost decrease), rather than when it realizes through a decrease in iceberg costs only. In maritime transport, where the decrease in total transport costs is larger (-6.4 percentage points), the extra welfare gain amounts to 1.12 percentage points when the transport cost reduction occurs through the additive component (by 50\%) rather than through the iceberg component only.\smallskip

@@

Figure \ref{fig:welfare_decomp} displays the welfare change and its decomposition between its two components following the reduction in international transport costs, for the decrease estimated in air transport (left column, Panels (1), (1-a) and (1-b)) and in maritime transport (right column, Panels (2), (2-a) and (2-b)). All are expressed in percentage change from the initial steady-state value. In each panel, the blue left bar displays the case where the trade liberalization occurs through a reduction in ad-valorem costs; the grey right bar reporting the case where the (same) reduction in international transport costs occurs through a combined reduction in both the ad-valorem and the additive components, based on our estimated results in 1974 and 2019 (for each transport mode), as in Table \ref{tab:calib_TC}).

@@

\subsubsection{Reducing fixed export costs}

The above results underline the importance of the additive component of international trade costs. Trade liberalization still has positive welfare effects, and even larger when it relies on a reduction in additive costs. One might question the robustness of this last result to the type of trade liberalization considered. Indeed, the reduction in the fixed export costs seems empirically relevant to account for the larger share of exporting firms nowadays relative to the 1970s (Based on XXX, from 19\% in XXX to around 35\% in XXX). As underlined by \cite{melitz} \textbf{l'a-t-il MONTRE VRAIMENT ANALYTIQUEMENT? A VERIFIER}, the reduction of the fixed export cost is also welfare-enhancing, in presence of yet only ad-valorem variable trade costs. A natural question then emerges: To what extent is this result modified in presence of additive costs? Specifically, are the welfare gains of a fixed export costs decrease larger in presence of additive costs?

The answer can be found in Table \ref{tab:resultats_modele}, by comparing Columns (B) to (D) for Air, (F) to (H) for Vessel, the difference between these two columns (for each transport mode) being the lower value of the fixed export cost. Here again, the welfare gains of trade liberalization (under the form of a lower fixed export cost) are larger when variable trade costs involve a part of additive costs: If the effect are quantitatively modest in maritime transport (by 0.75 percentage points, from 3.3\% to 4.05\%), the decrease in the fixed export cost is more sizeable when variable costs are lower, as in air transport where the welfare gains almost double (from 1.82\% to 3.25\%).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele_decompwelfare}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
%$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
%$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
%$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
%$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\ \hline
Variety effect (\%)&	-0.827	&0.747	&-2.670&	-1.132	&-1.323	&-0.126&	-3.061	& -1.857 \\
Price effect (\%)&	2.084&	1.455	&5.202&	4.444&	3.568	&3.001&	6.829&	6.059 \\ 
\hline
\end{tabular}
\end{center}
%{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: The reduction in transport costs is expressed in percentage points. }}}
\end{table}

>>>>

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs have strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings in two different ways.

First, we run a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario \textit{\grave{a} la M\'{e}litz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario \textit{\grave{a} la Hummels}, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components. Importantly, we run this comparative statics analysis \textit{ceteris paribus}, notably with the same value of the export fixed cost $f_x$ as in the initial equilibrium (see Table \ref{tab:calib_horsTC}.

@@

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (1)-(4)) and Vessel (Columns (5)-(8)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (A)-(B) for Air, (E)-(F) for Vessel), contrasting the case of only ad-valorem costs (Columns (A), (D)) and in presence of additive costs (Columns (B), (F)). Columns (C)-(D) for Air and (G)-(H) for Vessel report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3& 0&	-3.3 \\ \hline
$\Delta \mathcal{W}$ & 0.0202 &  0.0386 & 0.0362 & 0.0540 & 0.0354 & 0.0535 & 0.0467 & 	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	2.393 &	2.207	&3.348	&2.179	&3.382 &	2.872&	4.00   \\\hline
Variety effect (\%)&	-0.827 	&-2.599	&0.747
&-1.038	&-1.323	& -3.123&	-0.126	&-1.902 \\
Price effect (\%)&	2.084 &5.201	& 1.455 &	4.444&	3.568	& 6.829&	 3.001&	6.059 \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In the world including additive costs, we simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

\paragraph{Reduction in international variable transport costs} Based on our empirical estimates, we simulate a reduction in total variable transport costs by 3.4\% in Air transport and 6.4\% in maritime transport, in two different worlds: In a world with only ad-valorem costs (Columns (A) for Air and (D) for Vessel), versus a world with both iceberg and additive transport costs, and where the overall reduction costs comes from both components (Columns (B) for Air and (E) for Vessel).

A first conclusion emerges. Whatever the transport mode (and the associated magnitude of the transport costs decrease), trade liberalization induces welfare gains. Second, the welfare gains are higher when this reduction is partly achieved through a reduction of additive costs. The effect is substantial: The reduction variable transport costs generates a relative welfare gain higher by 1.1 percentage point in Air, 1.2 percentage point in Vessel, when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in iceberg costs only.\smallskip

@@

We report the decomposition of the welfare gains in their two components (under the various scenarii) in the last two lines of Table \ref{tab:resultats_modele}, as well as visually through Figure \ref{fig:welfare_decomp}. It displays the welfare change and its decomposition between its two components following the reduction in international transport costs, for the decrease estimated in air transport (left column, Panels (1), (1-a) and (1-b)) and in maritime transport (right column, Panels (2), (2-a) and (2-b)). All are expressed in percentage change from the initial steady-state value. In each panel, the blue left bar displays the case where the trade liberalization occurs through a reduction in ad-valorem costs; the grey right bar reporting the case where the (same) reduction in international transport costs occurs through a combined reduction in both the ad-valorem and the additive components, based on our estimated results in 1974 and 2019 (for each transport mode), as in Table \ref{tab:calib_TC}).

@@

\paragraph{Reduction of the fixed export cost} The above results underline the importance of the additive component of international trade costs. When trade liberalization occurs through a reduction in variable costs, not only the welfare-enhancing effects still apply, but they are even larger. As mentioned by Mélitz final proofs, the reduction in variable costs is not the only form of trade liberalization, which can typically manifest through a reduction in export fixed costs. One might then wonder how additive costs do affect the welfare gains of trade liberalization of this form. Indeed, the reduction in the fixed export costs seems empirically relevant to account for the larger share of exporting firms nowadays relative to the 1970s (Based on XXX, from 19\% in XXX to around 35\% in XXX). As underlined by \cite{melitz} \textbf{JE CROIS QUE C'est DIT DANS FINAL PROOFS, PAS ECTRA. l'a-t-il MONTRE VRAIMENT ANALYTIQUEMENT? A VERIFIER}, the reduction of the fixed export cost is also welfare-enhancing, in presence of yet only ad-valorem variable trade costs. A natural question then emerges: To what extent is this result modified in presence of additive costs? Specifically, are the welfare gains of a fixed export costs decrease larger in presence of additive costs?

The answer can be found in Table \ref{tab:resultats_modele}. First, in accordance with \textbf{Mélitz}, the reduction in the fixed export costs adds an extra source of welfare gains. In the pure iceberg world, welfare gains amount to 2.2\% when both fixed and variable costs reduce (Column (C) for Air), vs a 1.23\% increase when only ad-valorem costs decrease (Column (A) for Air, a similar result applying for Vessel). The larger welfare gains under a combined reduction in the variable and fixed export costs remains in the world with additive costs (Columns (D) vs (B) for Air, (H) vs (E) for Vessel). Further, in both worlds (with or without additive costs), the reduction in the fixed export cost induces an extra welfare gains by around 1 percentage point in Air transport, 1.2 percentage point in maritime transport. Put it differently, the reduction in the fixed export cost does not seem to depend on the composition of the variable costs. In the end, the welfare gains are the highest when trade liberalization induces a combined reduction in both variable and fixed export costs, and when the reduction in the variable part implies a reduction in the additive component, as observed empirically.

In line with \cite{sorensen2014} and \cite{Irrazabal_2015}, our overall theoretical results point out the importance of taking into the additive components of international trade costs. On the positive side, we show that additive costs have a substantial impact on the extensive margin of trade, by affecting the composition of the basket of exported goods. This has important consequences in normative terms. Neglecting the role of additive costs in the theoretical models of trade leads to a substantial underestimation of the welfare gains of trade liberalisation. Relying on our empirical estimates of transport costs over 1974-2019, we obtain that the 3.4\% reduction of variable costs in Air transport, combined to the reduction in the fixed export costs, has induced an 3.5\% increase in welfare, much higher than if only iceberg costs were modeled (2.4\%). A similar result applies with the observed 6.4\% in total variable costs in maritime transport along with the reduction in the fixed export costs, with a relative increase in welfare by 4\% (as compared to 3.38\% in a pure ad-valorem world).
